\textbf{Rete Convoluzionale per Image Deblurring}

### 2025-06-18 docs/paper.tex
paper

@@

@@

    \centering
    \subfloat[boh]{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/20250503_184657.jpg}
    }\hspace{0.1cm}\hfill
    \subfloat[boh]{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/20250503_184657_deblurred.jpg}
    }\hspace{0.1cm}\hfill
    \subfloat[boh]{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/comparison_20250503_184657.jpg}
    }\hspace{0.1cm}\hfill
    \\
    \subfloat[boh]{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/20250503_184720.jpg}
    }\hspace{0.1cm}\hfill
    \subfloat[boh]{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/20250503_184720_deblurred.jpg}
    }\hspace{0.1cm}\hfill
    \subfloat[boh]{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/comparison_20250503_184720.jpg}
    }\hspace{0.1cm}\hfill
    \\
    \subfloat[boh]{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/20250503_185104.jpg}
    }\hspace{0.1cm}\hfill
    \subfloat[boh]{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/20250503_185104_deblurred.jpg}
    }\hspace{0.1cm}\hfill
    \subfloat[boh]{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/comparison_20250503_185104.jpg}
    }\hspace{0.1cm}\hfill
    \\
    \subfloat[boh]{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/20250503_185233.jpg}
    }\hspace{0.1cm}\hfill
    \subfloat[boh]{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/20250503_185233_deblurred.jpg}
    }\hspace{0.1cm}\hfill
    \subfloat[boh]{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/comparison_20250503_185233.jpg}
    }\hspace{0.1cm}\hfill
    \\

@@

% First plot: SSIM and PSNR
\begin{figure}[ht]
  \centering
  \begin{tikzpicture}
    \begin{axis}[
        width=0.9\linewidth,
        xlabel={epoch},
        ylabel={SSIM},
        xtick distance={400},
        enlarge x limits=false,
        enlarge y limits=false,
        grid=none,
        thick,
        axis y line*=left,
        axis x line*=bottom,
        legend style={
          at={(0.97,0.16)},
          anchor=south east,
          cells={align=left},
          font=\scriptsize
        }
      ]
      % SSIM on left y-axis
      \addplot[blue, thick] table[x index=0, y index=1] {figures/validation_metrics_ssim.txt};
      \addlegendentry{SSIM}
    \end{axis}

    % Second axis overlay for PSNR
    \begin{axis}[
        width=0.9\linewidth,
        xlabel={epoch},
        ylabel={PSNR},
        xtick=\empty, % don't duplicate xticks
        yticklabel style={text=red},
        ylabel style={text=red},
        axis y line*=right,
        axis x line=none,
        xmin=0, xmax=2000, % or whatever the full range is
        grid=none,
        thick,
        legend style={
          at={(0.97, 0.03)},
          anchor=south east,
          cells={align=left},
          font=\scriptsize
        }
      ]
      % PSNR on right y-axis
      \addplot[red, thick, dashed] table[x index=0, y index=1] {figures/validation_metrics_psnr.txt};
      \addlegendentry{PSNR}
    \end{axis}
  \end{tikzpicture}

  \caption{Metriche: SSIM (a sinistra) e PSNR (a destra) su epochs.}
  \label{fig:ssim_psnr_dual}
\end{figure}

% Second plot: Content loss and Frequency loss
\begin{figure}[ht]
  \centering
  \begin{tikzpicture}
    % Left axis: Content loss
    \begin{axis}[
        width=0.9\linewidth,
        xlabel={epoch},
        ylabel={Content Loss},
        tick label style={font=\scriptsize},  % Smaller x-axis labels
        xtick distance={400},
        %x tick label style={text width = 1.7cm, align = center, rotate = 70, anchor = north east}, % Optional: rotate for dense x values
        enlarge x limits=false,
        enlarge y limits=false,
        grid=major,
        xmajorgrids=false,
        ymajorgrids=true,
        axis y line*=left,
        axis x line*=bottom,
        legend style={
          at={(0.97,0.97)},
          anchor=south east,
          cells={align=left},
          font=\scriptsize
        }
      ]
      \addplot[green!60!black, thick] table[x index=0, y index=1] {figures/loss_content.txt};
      \addlegendentry{Content Loss}
    \end{axis}

    % Right axis: Frequency loss
    \begin{axis}[
        width=0.9\linewidth,
        ylabel={Frequency Loss},
        yticklabel style={text=orange, font=\scriptsize},
        ylabel style={text=orange},
        xtick=\empty,
        axis y line*=right,
        axis x line=none,
        grid=none,
        enlarge x limits=false,
        enlarge y limits=false,
        legend style={
          at={(0.97,0.84)},
          anchor=south east,
          cells={align=left},
          font=\scriptsize
        }
      ]
      \addplot[orange, thick, dashed] table[x index=0, y index=1] {figures/loss_frequency.txt};
      \addlegendentry{Frequency Loss}
    \end{axis}
  \end{tikzpicture}

  \caption{Training loss nelle epoche: Spatial Loss (a sinistra) and Frequency Loss (a destra).}
  \label{fig:dual_losses}
\end{figure}

>>>>

\usepackage{floatrow}

@@

\begin{figure*}[t]
  \centering

  \begin{floatrow}

  \subfloat[\centering Metriche di validazione: SSIM (a sinistra) e PSNR (a destra) su epochs.]{
    \begin{tikzpicture}[scale = 0.4]
    \begin{axis}[
        width=0.9\linewidth,
        xlabel={epoch},
        ylabel={SSIM},
        xtick distance={400},
        enlarge x limits=false,
        enlarge y limits=false,
        grid=none,
        thick,
        axis y line*=left,
        axis x line*=bottom,
        legend style={
          at={(0.97,0.16)},
          anchor=south east,
          cells={align=left},
          font=\scriptsize
        }
      ]
      % SSIM on left y-axis
      \addplot[blue, thick] table[x index=0, y index=1] {figures/validation_metrics_ssim.txt};
      \addlegendentry{SSIM}
    \end{axis}

    % Second axis overlay for PSNR
    \begin{axis}[
        width=0.9\linewidth,
        xlabel={epoch},
        ylabel={PSNR},
        xtick=\empty, % don't duplicate xticks
        yticklabel style={text=red},
        ylabel style={text=red},
        axis y line*=right,
        axis x line=none,
        xmin=0, xmax=2000, % or whatever the full range is
        grid=none,
        thick,
        legend style={
          at={(0.97, 0.03)},
          anchor=south east,
          cells={align=left},
          font=\scriptsize
        }
      ]
      % PSNR on right y-axis
      \addplot[red, thick, dashed] table[x index=0, y index=1] {figures/validation_metrics_psnr.txt};
      \addlegendentry{PSNR}
    \end{axis}
    \end{tikzpicture}
  }

  \subfloat[\centering Training loss nelle epoche]{
    \begin{tikzpicture}[scale = 0.4]
    % Left axis: Content loss
    \begin{axis}[
        width=0.9\linewidth,
        xlabel={epoch},
        ylabel={Loss},
        tick label style={font=\scriptsize},  % Smaller x-axis labels
        xtick distance={400},
        %x tick label style={text width = 1.7cm, align = center, rotate = 70, anchor = north east}, % Optional: rotate for dense x values
        enlarge x limits=false,
        enlarge y limits=false,
        grid=major,
        xmajorgrids=false,
        ymajorgrids=true,
        axis y line*=left,
        axis x line*=bottom,
      ]
      \addplot[blue!60!black, thick] table[x index=0, y index=1] {figures/out.txt};
      \end{axis}
    \end{tikzpicture}
  }

  \end{floatrow}

  \label{fig:metrics}
\end{figure*}

@@

    \centering
    \subfloat{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/20250503_184657.jpg}
    }\hspace{0.1cm}\hfill
    \subfloat{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/20250503_184657_deblurred.jpg}
    }\hspace{0.1cm}\hfill
    \subfloat{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/comparison_20250503_184657.jpg}
    }\hspace{0.1cm}\hfill
    \\ \vspace{0.3cm}
    \subfloat{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/20250503_184720.jpg}
    }\hspace{0.1cm}\hfill
    \subfloat{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/20250503_184720_deblurred.jpg}
    }\hspace{0.1cm}\hfill
    \subfloat{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/comparison_20250503_184720.jpg}
    }\hspace{0.1cm}\hfill
    \\ \vspace{0.3cm}
    \subfloat{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/20250503_185104.jpg}
    }\hspace{0.1cm}\hfill
    \subfloat{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/20250503_185104_deblurred.jpg}
    }\hspace{0.1cm}\hfill
    \subfloat{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/comparison_20250503_185104.jpg}
    }\hspace{0.1cm}\hfill
    \\ \vspace{0.3cm}
    \subfloat{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/20250503_185233.jpg}
    }\hspace{0.1cm}\hfill
    \subfloat{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/20250503_185233_deblurred.jpg}
    }\hspace{0.1cm}\hfill
    \subfloat{
      \centering\includegraphics[width=0.31\linewidth]{figures/sample_imgs/comparison_20250503_185233.jpg}
    }\hspace{0.1cm}\hfill
    \\ \vspace{0.3cm}

@@
